### 2021-04-19 evaluation.tex
Add some Oxford commas

To ensure the efficiency of the sampling, we interpreted the process as an instance of the Bernoulli multi-armed bandit problem \cite{Sutton1998},
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balanced
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was bootstrapped with is
$n_0 = \ceil{\frac{2 \log{N}}{\Parentheses{1 + \sqrt{\frac{2 \log{N} \card{\ProblemsTptp}}{N}}}^2}}$,
where $N$ is the final number of examples to be generated.
For example, if $N=1000000$ and $\card{\ProblemsTptp}=17053$, then $n_0 = 10$.}
% FB: Note that the original UCB1 initially samples each object exactly once.
% FB: More precisely, N can be any lower bound on the number of tries to be performed.
\todo[inline,author=FB,disable]{We bootstrap with a per-problem lower bound on the final number of questions. The lower bound is a solution to the equation for $n_B$:

>>>>

To ensure the efficiency of the sampling, we interpreted the process as an instance of the Bernoulli multi-armed bandit problem \cite{Sutton1998},
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balanced
exploring problems that have been tried relatively scarcely, and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$,
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was bootstrapped with is
$n_0 = \ceil{\frac{2 \log{N}}{\Parentheses{1 + \sqrt{\frac{2 \log{N} \card{\ProblemsTptp}}{N}}}^2}}$,
where $N$ is the final number of examples to be generated.
For example, if $N=1000000$ and $\card{\ProblemsTptp}=17053$, then $n_0 = 10$.}
% FB: Note that the original UCB1 initially samples each object exactly once.
% FB: More precisely, N can be any lower bound on the number of tries to be performed.
\todo[inline,author=FB,disable]{We bootstrap with a per-problem lower bound on the final number of questions. The lower bound is a solution to the equation for $n_B$:
